method

### 2021-08-25 06_Paper/ER-ED/method.Rmd
added imports

# set top level directory to source file
here::i_am("flag_project_root.txt")
```

@@

```{r stimvalues, echo = FALSE}

StimNeg

>>>>

# set top level directory to source file
here::i_am("flag_project_root_COGERED.txt")
```

@@

```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))

stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")))
